The SMT Competition 2015--2018

### 2019-08-22 2018/report/Reviews_67398_Revised_Response.txt

> (28), Tbl 7: Thanks for the revision of the table, but I'm not sure listing
> more team members to "the best of our knowledge" is a good idea. If I were to
> do that, I would be bound to miss someone... Maybe just list the main
> institution? Or perhaps ask the submitter who they would want to be listed? I
> think there should be enough time to do that.

TODO

> General: Gray and grey are the worst colors to use. On my (Xerox color-laser)
> printer, all of the gray text in tables and figures are almost or completely
> unreadable. For instance, on white (bleached) paper there is not even a faint
> trace of the gray vertical line in Figures 3/4; I had to switch to the screen
> to see what this refers to.

WONTFIX (we concede that gray text can be problematic with certain
printers; however, other colors can be equally problematic, and some
of the tables and figures contain a lot of information, which we find
difficult to condense without the use of color)

@@

> Fig 5/6: These could be significantly smaller :)

TODO

> Fig 3/4: Starting the X-axis at an arbitrary point is always a bit fishy. This
> way, any tiny difference can be overemphasized to achieve any level of
> impressiveness that the author choses. For instance, 144k vs 136k instances
> (casually read off the plot) is a 3.5% increase, but this is an irrelevant
> detail as explained in the text. All four series are also of exactly the same
> shape. I think a cactus plot is simply not the right tool for this job.

WONTFIX (starting the x-axis at 0 would render the plots unexpressive;
a cactus plot may not be ideal but we haven't been able to find a
better tool)

### 2019-08-22 2018/report/SMT-COMP.tex
focusses -> focuses

The SMT Competition is one of a growing number of tool competitions in the broad area of formal methods, which are summarised in a recent review of the area~\cite{toolympics}. The two closest competitions in terms of goals and design are the SAT competition (\url{http://www.satcompetition.org/}), which evaluates SAT solvers, and CASC (\url{http://www.tptp.org/CASC/}), which evaluates automated theorem provers (ATPs). In recent years, we have seen a blurring of lines between SMT-COMP and CASC with SMT solvers competing in CASC and ATPs competing in SMT-COMP. The main (informal) distinction remains that SMT-COMP focusses on problems that are heavy in theories, whereas CASC focusses on problems heavy in quantifiers.
Another closely related competition is SV-COMP (\url{https://sv-comp.sosy-lab.org}) where many tools rely on advances in SMT solving technology.

>>>>

The SMT Competition is one of a growing number of tool competitions in the broad area of formal methods, which are summarised in a recent review of the area~\cite{toolympics}. The two closest competitions in terms of goals and design are the SAT competition (\url{http://www.satcompetition.org/}), which evaluates SAT solvers, and CASC (\url{http://www.tptp.org/CASC/}), which evaluates automated theorem provers (ATPs). In recent years, we have seen a blurring of lines between SMT-COMP and CASC with SMT solvers competing in CASC and ATPs competing in SMT-COMP. The main (informal) distinction remains that SMT-COMP focuses on problems that are heavy in theories, whereas CASC focuses on problems heavy in quantifiers.
Another closely related competition is SV-COMP (\url{https://sv-comp.sosy-lab.org}) where many tools rely on advances in SMT solving technology.
